\documentclass[11pt,letterpaper]{article}

\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}

% formatting
\pagestyle{empty}
\setlength{\parindent}{0pt}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{6pt}
\setlist[itemize]{nosep,leftmargin=1.5em,topsep=2pt}

\hypersetup{colorlinks=true,urlcolor=blue!70!black}

\begin{document}

% ---------- HEADER ----------
\begin{center}
  {\LARGE\bfseries Vishnu Kadiyala}\\[4pt]
  Ph.D.\ Candidate, Computer Science $\cdot$ University of Oklahoma\\[2pt]
  \href{mailto:vishnupk@ou.edu}{vishnupk@ou.edu} \,|\,
  \href{https://github.com/vishnukadiyala}{GitHub} \,|\,
  \href{https://www.linkedin.com/in/vishnu-kadiyala/}{LinkedIn} \,|\,
  \href{https://scholar.google.com/citations?user=3Eh2neYAAAAJ}{Google Scholar} \,|\,
  \href{https://vishnu.kadiyala.net}{Portfolio}
\end{center}

% ---------- FOCUS ----------
\section{Research Focus}
Multi-Agent Reinforcement Learning under partial observability;
decentralized policy learning and implicit coordination via learned belief representations;
learned communication for cooperative multi-agent systems;
learning dynamics and optimization pathologies in cooperative MARL training;
applications to autonomous driving and V2X.

% ---------- EDUCATION ----------
\section{Education}

\textbf{University of Oklahoma}, Norman, OK \hfill Expected May 2027\\
Ph.D.\ in Computer Science\\[4pt]
\textbf{University of Oklahoma}, Norman, OK \hfill May 2022\\
M.S.\ in Electrical and Computer Engineering\\
\textit{Thesis: Localization of Tables and Plots in Documents Using Deep Neural Networks}\\[4pt]
\textbf{KLE Technological University}, India \hfill May 2019\\
B.E.\ in Electronics and Communication Engineering

% ---------- TECHNICAL EXPERTISE ----------
\section{Technical Expertise}

\textbf{Machine Learning:} Multi-Agent Reinforcement Learning, Deep Learning, Transformers, Attention Mechanisms, CNNs, U-Nets, Diffusion Models\\
\textbf{Deep Learning Frameworks:} PyTorch, JAX / Flax, TensorFlow, Keras\\
\textbf{Simulation Environments:} Highway-Env, MetaDrive, MPE (Speaker--Listener), SMAX, Overcooked\\
\textbf{Programming:} Python\\
\textbf{Data \& Compute:} HPC / SLURM, CUDA, Multi-Machine Orchestration (Tailscale + SSH), Pandas, NumPy, Xarray\\
\textbf{Tools:} Git / GitHub, Linux, Reproducible ML Pipelines

% ---------- RESEARCH EXPERIENCE ----------
\section{Research Experience}

\textbf{Multi-Agent RL Research --- University of Oklahoma} \hfill 2025 -- Present
\begin{itemize}
  \item \textbf{Submitted to NeurIPS 2026:} \textit{When Auxiliary Losses Fail: Non-Stationary Targets Induce Directional Gradient Noise.} Characterized a gradient-interference pathology in attention + auxiliary-loss architectures across both cooperative MARL and supervised learning. \textbf{290+ runs across 7 experiments}; three architectural fixes (stop-gradient on the auxiliary target, $\lambda$-annealing, mean-pool attention) recover lost performance.
  \item Cross-domain validation across Overcooked, Simple, and SMAX (MARL) and CIFAR-100 (vision), demonstrating the pathology is not RL-specific.
  \item Designed evaluation protocols that distinguish coordination from coincidence: ablations, counterfactual tests, and seed-pooled population estimators.
  \item Developing \textbf{AwareGate} (in progress, ICLR 2027 target): learned communication-gating policy combining cross-attention message fusion with a recurrent belief state, for cooperative multi-agent systems including V2X.
\end{itemize}

\medskip

\textbf{NSF AI2ES --- ML Researcher} (\href{https://github.com/ai2es/ZR-relationship}{GitHub}) \hfill 2023 -- 2025
\begin{itemize}
  \item Built a \textbf{Transformer-based} architecture with custom spatial / temporal embeddings for multi-modal irregular spatio-temporal data (ground stations + radar + satellite), achieving a \textbf{13$\times$ improvement} over the classical Marshall--Palmer baseline.
  \item Developed a \textbf{vision-based atmospheric visibility estimation} system using outdoor camera imagery for statewide inference beyond sparse ASOS sensor coverage.
  \item Designed and maintained reproducible ML training and evaluation pipelines on HPC infrastructure for large-scale multi-modal sensor datasets.
  \item Co-authored peer-reviewed paper: \textit{Estimating Statewide Atmospheric Visibility From Camera Images} (AMS 2025).
\end{itemize}

\medskip

\textbf{NASA GeoCARB --- Deep Learning Researcher} (\href{https://github.com/GeoCarb-OU/methane_hotspot_detection}{GitHub}) \hfill 2021 -- 2023
\begin{itemize}
  \item Designed \textbf{U-Net} architectures for methane hotspot detection from satellite imagery, achieving \textbf{95\% accuracy}.
  \item Improved anomaly detection from 80\% to \textbf{90.2\%} using diffusion-based generative models on satellite observations.
  \item Built data-quality assessment frameworks for satellite observation datasets including preprocessing validation, augmentation strategies, and quality assurance pipelines.
\end{itemize}

\medskip

\textbf{Document Understanding with Deep Learning} \hfill Aug 2021 -- May 2022
\begin{itemize}
  \item Designed CNN-based architectures for \textbf{object detection and localization} of tables and plots in documents, achieving \textbf{99\% detection accuracy}.
  \item Constructed annotated datasets with bounding-box labels and automated document generation pipelines for scalable training data.
  \item \textit{Master's Thesis: Localization of Tables and Plots in Documents Using Deep Neural Networks.}
\end{itemize}

% ---------- PUBLICATIONS ----------
\section{Selected Publications}

\textbf{Under Review}
\begin{itemize}
  \item \textbf{V.\ P.\ Kadiyala}. \textit{When Auxiliary Losses Fail: Non-Stationary Targets Induce Directional Gradient Noise.} Under review at NeurIPS 2026.
\end{itemize}

\textbf{Peer-Reviewed Conference Papers}
\begin{itemize}
  \item M.\ X.\ Sasser, M.\ Wilson Reyes, \textbf{V.\ P.\ Kadiyala}, A.\ Kurbanovas, K.\ J.\ Sulia, et al. \textit{Estimating Statewide Atmospheric Visibility From Camera Images.} Proceedings of the 105th AMS Annual Meeting, 2025.
  \item E.\ Spicer, S.\ Crowell, F.\ Xu, \textbf{V.\ P.\ Kadiyala}, P.\ M.\ Klein, et al. \textit{Exploring the Influence of Local Urban and Industrial Carbon-Based Pollutant Sources on Total Column Concentration Enhancements in Houston, Texas during TRACER.} Proceedings of the 104th AMS Annual Meeting, 2024.
\end{itemize}

\textbf{Theses}
\begin{itemize}
  \item \textbf{V.\ P.\ Kadiyala}. \textit{Localization of Tables and Plots in Documents Using Deep Neural Networks.} Master's Thesis, University of Oklahoma, 2022.
\end{itemize}

% ---------- TEACHING ----------
\section{Teaching}

\textbf{Teaching Assistant --- CS 2614 Computer Organization}, University of Oklahoma \hfill 2024 -- Present
\begin{itemize}
  \item Lead weekly hands-on labs on digital logic, assembly-level programming, and hardware / software interface fundamentals.
  \item Develop lab documentation, debugging workflows, and troubleshooting guides; provide one-on-one mentoring across varied skill levels.
\end{itemize}

% ---------- INDUSTRY EXPERIENCE ----------
\section{Industry \& Engineering Experience}

\textbf{Test Automation Intern --- Robert Bosch Engineering \& Business Solutions} \hfill Jan 2019 -- May 2019
\begin{itemize}
  \item Developed hardware-in-the-loop (HIL) test automation pipelines for Engine Control Units (ECUs).
  \item Automated ECU software validation using ETAS LABCAR across hardware and digital fault layers.
\end{itemize}

\end{document}
